results

### 2022-04-11 code/analysis_code/density.Rmd
sunday updates

```{r}
df <- tracts(state = 'GA', county = c('Clarke'), )
plot(df)
```
The GEOID in the df dataframe matches our FIPS code for the population/sample data. Let's add the land area variable to the tractpopdata dataframe and then mutate a new variable to calculate population density. Then, we can compare population density to MP concentration.

@@

>>>>

```{r}
df_clarke <- tracts(state = 'GA', county = c('Clarke'))
plot(df_clarke)

df <- tracts(state = 'GA', county = c('Clarke', 'Oconee'))
```
The GEOID in the df dataframe matches our FIPS code for the population/sample data. Let's add the land area variable to the tractpopdata dataframe and then mutate a new variable to calculate population density. Then, we can compare population density to MP concentration.

@@

#land cover distribution
```{r}
land_long <- athensland %>% pivot_longer(12:26)

land_long %>% ggplot(aes(x = name, y = value)) + geom_col() + 
  theme(axis.text.x = element_text(angle = 45, hjust=1))
```

### 2022-04-11 code/analysis_code/particle_type.Rmd
sunday updates

 # here is some code for adding % labels, but I can't get it to work without messing up the graph                                                       #geom_text(aes(label=paste0(sprintf("%1.1f", percent*100),"%")),
                   #  position=position_stack(vjust=0.5), colour="white", size = 2)  
```

>>>>

 # here is some code for adding % labels, but I can't get it to work without messing up the graph                                                       #geom_text(aes(label=paste0(sprintf("%1.1f", percent*100),"%")),
                   #  position=position_stack(vjust=0.5), colour="white", size = 2)  
```
# particle type by water body
```{r}
ggplot(data = part_sum, aes(x = body, y = value, fill = name)) + geom_bar(stat = "identity", position = "fill") + labs(x = "", y = "Microplastic Composition") + guides(fill=guide_legend("Particle Color")) +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
```

### 2022-04-11 code/analysis_code/results.Rmd
sunday updates

#load packages and data
```{r}
library(ggplot2) #for plotting
library(broom) #for cleaning up output from lm()
library(here) #for data loading/saving
library(tidymodels) #for modeling
library(gridExtra) #for exporting tables
library(gridExtra) #for savings images in grids
library(dplyr)
library(gridExtra) #for savings images in grids
library(gridExtra) #for savings images in grids

@@

@@

#plot
body %>% ggplot(aes(x = body, y = particles_l, color = )) + 
  geom_boxplot()  +
  theme(axis.text.x = element_text(angle = 45, hjust=1)) +
  labs(title = "Microplastic Concentration by Water Body", x = "Water Body", y = "Particles/Liter") + ylim(0,500) + scale_y_log10()

#kruskal wallis/mann whitney test - nonparametric test
kruskal.test(particles_l ~ body, data = body)
```

>>>>

#load packages and data
```{r}
library(ggplot2) #for plotting
library(broom) #for cleaning up output from lm()
library(here) #for data loading/saving
library(tidymodels) #for modeling
library(gridExtra) #for exporting tables
library(gridExtra) #for savings images in grids
library(dplyr)
library(gridExtra) #for savings images in grids
library(gridExtra) #for savings images in grids
library(ggpubr) #adding stats to figures

@@

#adding stats to graph
```{r}
ggplot(all_counts_cv, aes(x = particles_l, y = cv)) + geom_point() +
  stat_cor(method = "spearman")

ggplot(all_counts_cv, aes(x = particles_l, y = cv)) + geom_point() + geom_smooth(method = lm) + labs(title = "Coefficient of Variance vs. Microplastic Concentration ", x = "Particles/L", y = "Coefficient of Variance %") +
  stat_cor(method = "spearman") + scale_x_continuous(trans='log10') # use log scale to better visualize all points

df %>% ggplot(aes(x = x , y = y)) +
  geom_point() +
  stat_cor(method = "spearman")

  geom_smooth(method = lm) + labs(title = "Coefficient of Variance vs. Microplastic Concentration ", x = "Particles/L", y = "Coefficient of Variance %") + scale_x_continuous(trans='log10') # use log scale to better visualize all points

figure_s1_data %>% ggplot(aes(x = cases.reported.7dma/1.2, y = value)) +
  geom_point() +
  facet_grid(variable~target, scales = "free",  labeller = label_wrap_gen()) +
  stat_cor(method = "spearman") +
  ylab("Value") +
  xlab("Reported Cases per 100K (7-Day Moving Average)")

```

@@

#plot
body %>% ggplot(aes(x = body, y = particles_l, color = )) + 
  geom_boxplot()  +
  theme(axis.text.x = element_text(angle = 45, hjust=1)) +
  labs(title = "Microplastic Concentration by Water Body", x = "Water Body", y = "Particles/Liter") + ylim(0,500) + scale_y_log10() +
  stat_cor(method = "spearman")

#kruskal wallis/mann whitney test - nonparametric test
kruskal.test(particles_l ~ body, data = body)
wilcox.test(particles_l ~ body, data = body)

summary(river)
summary(trib)
```
